\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-01 paper.tex
merge:
trim
fix some writing

A canonical distribution bridges an energy with a probability distribution.
If two different states have the same energy, the probabilities of them are equivalent.
A set of samples from such a distribution can be equivalent to a set of samples driven by an associated energy.
By using the system energy $ H(x, q) $, we can defines a canonical distribution $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
Because $ H(x,q) = U(x) + K(q) $, $ P(x, q) $ can be factorized into two independent terms, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -U(x) / T) \exp (-K(q) / T) $.
The independence implies that we can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable) in order to sample from a canonical distribution $ \propto \exp ( -U(x) / T) $.
If we have a target distribution $ \pi(x) $ of state $ x $ and define a potential energy in the form $  U(x) = - \log ( \pi(x) T ) $, we can have the canonical distribution equal to $ \pi(x) $.
The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.
Thus, we can use simulating the Hamiltonian dynamics to generate a set of samples from a target distribution $ \pi (x) $.

>>>>

A canonical distribution bridges an energy with a probability distribution.
If two different states have the same energy, the probabilities of them are equivalent.
A set of samples from such a distribution can be equivalent to a set of samples driven by an associated energy.
By using the system energy $ H(x, q) $, we can defines a canonical distribution $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
We can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable) in order to sample from a marginal distribution $ P(x) $.
If we have a target distribution $ \pi(x) $ of state $ x $ and define a potential energy in the form $  U(x) = - \log ( \pi(x) T ) $, we can have the canonical distribution equal to $ \pi(x) $.
The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.
Thus, we can use simulating the Hamiltonian dynamics to generate a set of samples from a target distribution $ \pi (x) $.
The properties of Hamiltonian dynamics guarantees so that the proposals will always be accepted, which accelerates the convergence rate.
